Saint Helena Island Implementation

### 2024-10-21 Implementation doc/Draft1.Rmd
modifications tables in the doc

```{r domain, echo=FALSE, fig.cap="Map of the model domain. StrathE2E defines seabed sediment habitats as inshore (light gray) or offshore/overhang (dark gray). Within each zone, three sediment classes can be represented -- fine (muddy, 1), medium (sandy, 2) and coarse (gravel, 3). A fourth class (rock, 0) represents an absence of soft sediment. Note that the majority of the Saint Helena model domain is comprised by the "overhang", which does not contact the sea floor.", out.width = '100%'}
knitr::include_graphics("img/domain.png")
```

@@

data_frame(Property = c("Sea-surface area proportion",
                        "Upper layer thickness (m)",
                        "Lower layer thickness (m)"),
           `Inshore/shallow` = c(model[["data"]][["physical.parameters"]][["x_shallowprop"]], 
                                 model[["data"]][["physical.parameters"]][["si_depth"]], 
                                 NA),
           `Offshore/deep` = c(1 - model[["data"]][["physical.parameters"]][["x_shallowprop"]], 
                               model[["data"]][["physical.parameters"]][["so_depth"]], 
                               model[["data"]][["physical.parameters"]][["d_depth"]])) %>% 
  gt() %>% 
  fmt_number(columns = c("Offshore/deep", "Inshore/shallow"), decimals = 4, use_seps = FALSE)

@@

data_frame(Habitat = c("S0", "S1", "S2", "S3", "D0", "D1", "D2", "D3", "OV"),
           Depth = depth_vector,
           Zone = zone_vector,
           Sediment = rep(c("None (Rock)", "Fine", "Medium", "Coarse", "None (Rock)", "Fine", "Medium", "Coarse", "Overhang")),
           `Area Proportion` = physical$Value[proportions],
           `Grain size` = c(0, physical$Value[grain[1:3]], 0, physical$Value[grain[4:6]], NA),
           Porosity = c(NA, physical$Value[porosity[1:3]], NA, physical$Value[porosity[4:6]], NA),
           Permeability = c(NA, physical$Value[permeability[1:3]], NA, physical$Value[permeability[4:6]], NA),
           `Nitrogen content` = c(NA, physical$Value[nitrogen[1:3]], NA, physical$Value[nitrogen[4:6]], NA)) %>% 
  group_by(Zone, Depth) %>% 
  gt() %>% 
  fmt_number(columns = c("Area Proportion", "Grain size", "Porosity", "Permeability", "Nitrogen content"), 
                         decimals = 4, use_seps = FALSE) %>% 
  cols_align(align = 'center',
             columns = vars(`Area Proportion`, `Grain size`, Porosity, Permeability, `Nitrogen content`)) %>% 
  tab_options(row_group.background.color = "whitesmoke")

@@

tab <- production_tab %>%
  gt() %>%
  fmt_number(
    columns = vars(`P/B`, `mMN convertion`, `Production(t)`),
    decimals = 2,
    use_seps = FALSE
  ) %>%
  fmt_number(
    columns = vars(`Production (mMN.m-2)`),
    decimals = 6,
    use_seps = FALSE
  ) %>%
  tab_options(
    table.font.size = 11,
    column_labels.font.weight = "bolder",
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  cols_label(
    Guild = "Guild",
    `P/B` = "P/B",
    `Production(t)` = "Production(t)",
    `mMN convertion` = "mMN convertion",
    `Production (mMN.m-2)` = html("Production (mMN.m<sup>-2</sup>)")
  )
tab
```

@@

## Acknowledgements {.unnumbered}

@@

## Appendix {.unnumbered}

@@

```{r read_csv}
apply_group_style <- function(gt_table, group_name, start_row, end_row) {
  gt_table %>%
    tab_row_group(
      group = group_name,
      rows = start_row:end_row) %>%
    tab_style(
      style = list(cell_fill(color = "#D3D3D3"),
        cell_text(weight = "bold", align = "left")),
      locations = cells_row_groups(groups = group_name))
}

>>>>

```{r domain, echo=FALSE, fig.cap="Map of the model domain. StrathE2E defines seabed sediment habitats as inshore (light gray) or offshore/overhang (dark gray). Within each zone, three sediment classes can be represented -- fine (muddy, 1), medium (sandy, 2) and coarse (gravel, 3). A fourth class (rock, 0) represents an absence of soft sediment. Note that the majority of the Saint Helena model domain is comprised by the 'overhang', which does not contact the sea floor.", out.width = '100%'}
knitr::include_graphics("img/domain.png")
```

@@

tibble(Property = c("Sea-surface area proportion",
                        "Upper layer thickness (m)",
                        "Lower layer thickness (m)"),
           `Inshore/shallow` = c(model[["data"]][["physical.parameters"]][["x_shallowprop"]], 
                                 model[["data"]][["physical.parameters"]][["si_depth"]], 
                                 NA),
           `Offshore/deep` = c(1 - model[["data"]][["physical.parameters"]][["x_shallowprop"]], 
                               model[["data"]][["physical.parameters"]][["so_depth"]], 
                               model[["data"]][["physical.parameters"]][["d_depth"]])) %>% 
  gt() %>% 
  fmt_number(columns = c("Offshore/deep", "Inshore/shallow"), decimals = 4, use_seps = FALSE)

@@

data_frame(Habitat = c("S0", "S1", "S2", "S3", "D0", "D1", "D2", "D3", "OV"),
           Depth = depth_vector,
           Zone = zone_vector,
           Sediment = rep(c("None (Rock)", "Fine", "Medium", "Coarse", "None (Rock)", "Fine", "Medium", "Coarse", "Overhang")),
           `Area Proportion` = physical$Value[proportions],
           `Grain size` = c(0, physical$Value[grain[1:3]], 0, physical$Value[grain[4:6]], NA),
           Porosity = c(NA, physical$Value[porosity[1:3]], NA, physical$Value[porosity[4:6]], NA),
           Permeability = c(NA, physical$Value[permeability[1:3]], NA, physical$Value[permeability[4:6]], NA),
           `Nitrogen content` = c(NA, physical$Value[nitrogen[1:3]], NA, physical$Value[nitrogen[4:6]], NA)) %>% 
  group_by(Zone, Depth) %>% 
  gt() %>% 
  fmt_number(columns = c("Area Proportion", "Grain size", "Porosity", "Permeability", "Nitrogen content"), 
                         decimals = 4, use_seps = FALSE) %>% 
  cols_align(align = 'center',
             columns = c(`Area Proportion`, `Grain size`, Porosity, Permeability, `Nitrogen content`)) %>% 
  tab_options(row_group.background.color = "whitesmoke")

@@

tab <- production_tab %>%
  gt() %>%
  fmt_number(
    columns = c(`P/B`, `mMN convertion`, `Production(t)`),
    decimals = 2,
    use_seps = FALSE
  ) %>%
  fmt_number(
    columns = c(`Production (mMN.m-2)`),
    decimals = 6,
    use_seps = FALSE
  ) %>%
  tab_options(
    table.font.size = 11,
    column_labels.font.weight = "bolder",
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  cols_label(
    Guild = "Guild",
    `P/B` = "P/B",
    `Production(t)` = "Production(t)",
    `mMN convertion` = "mMN convertion",
    `Production (mMN.m-2)` = html("Production (mMN.m<sup>-2</sup>)")
  )
tab
```

@@

### Acknowledgements {.unnumbered}

@@

### Appendix {.unnumbered}

@@

```{r read_csv}
apply_group_style <- function(gt_table, group_name, start_row, end_row) {
  gt_table %>%
    tab_row_group(
      label = group_name,
      rows = start_row:end_row) %>%
    tab_style(
      style = list(cell_fill(color = "#D3D3D3"),
        cell_text(weight = "bold", align = "left")),
      locations = cells_row_groups(groups = group_name))
}
